A Critical Review of Sophistication and Model Selection in Algorithmic Statistics

### 2014-12-08 Facticity/Facticity/paper.tex
flupsie

>>>>

\section{Paul's sophistication (total, non-prefix) is \emph{not}  bounded}

Proof sketch:

\begin{itemize}
  \item From \cite[Proposition~I.3 (b)]{gacs2001algorithmic} we know
    that for sufficiently large $n$ there are strings of length less
    than $n$ that are not $(n/4, n/4)$-stochastic.
  \item By definition of $(\alpha,\beta)$-stochasticity, if a string
    is not $(n/4,n/4)$-stochastic, then for every finite set $S$,
    either (a) $\log|S|\ge K(x)+n/4$, so $S$ cannot be a candidate
    representation for $x$, or (b) $K(S)>n/4$. For sufficiently large
    $n$, we have $n/4>K(x)/5$, so we also know $K(S)>K(x)/5$.
  \item Neem nonstochastic string zoals hierboven beschreven. Stel dat
    die een total candidate heeft met klein model. Dan kun je de
    reductie naar sets doen ter betaling van $\log(n)$ additieve term,
    en dan heb je dus ook een kleine finite-set representatie, maar
    dat is een tegenspraak. QED
  \item De reductie van total naar finite sets staat (met typo's) in
    \cite[Lemma~7.2]{vitanyi2004meaningful}. 
\end{itemize}
